---
title: "Setup & First steps with Git"
subtitle: "Session 03"
date: 2024-09-27T10:45:00
metadata-files:
  - _sessions.yml
about:
  id: hero-heading
  template: solana
  image-width: 0em
  links:
    - icon: display
      text: Slides
      href: https://lennartwittkuhn.com/version-control-course-mpib-2024/sessions/slides_session03.html
      aria-label: display
    # - icon: book
    #   text: "Chapter: Installation"
    #   href: https://lennartwittkuhn.com/version-control-book/chapters/installation.html
    #   aria-label: book
    - icon: book
      text: "Chapter: Setup"
      href: https://lennartwittkuhn.com/version-control-book/chapters/setup.html
      aria-label: book
    - icon: book
      text: "Chapter: First steps with Git"
      href: https://lennartwittkuhn.com/version-control-book/chapters/first-steps-git.html
      aria-label: book
    # - icon: input-cursor-text
    #   text: "Survey: Installation"
    #   href: https://version-control-installation.formr.org
    #   aria-label: input-cursor-text
    - icon: input-cursor-text
      text: "Survey: Git Basics"
      href: https://version-control-basics.formr.org/
      aria-label: input-cursor-text
chapter-title: "First steps with Git"
chapter-url: https://lennartwittkuhn.com/version-control-book/chapters/first-steps-git.html
quiz-url: https://version-control-basics.formr.org/
---

::: {#hero-heading}
:::

## This session

In this session, you will work on the following tasks:

1. {{< fa book-open >}} **Reading**: Read the chapters ["Setup"](https://lennartwittkuhn.com/version-control-book/chapters/setup.html) and ["First steps with Git"](https://lennartwittkuhn.com/version-control-book/chapters/first-steps-git.html) in the Version Control Book.
1. {{< fa laptop-code >}} **Implementation**: Try out the commands in the chapter.
1. {{< fa laptop-code >}} **Exercises**: Work on the [exercises](#exercises) for the [`recipes` project](#recipes-project).
1. {{< fa clipboard-question >}} **Quiz**: Test your knowledge with the [quiz]({{< meta quiz-url >}}).

As always:

1. Try out the commands of this session and play around with them.
1. Check whether you have achieved the [learning objectives](#learning-objectives).
1. Ask questions!
1. Let's *git* started!

## Learning objectives

### Setup

{{< include ../objectives/_objectives-setup.qmd >}}

### First steps with Git

{{< include ../objectives/_objectives-firststeps.qmd >}}

## `recipes` project

{{< include recipes/recipes-basics.qmd >}}

## Exercises

{{< include ../exercises/_exercises-setup.qmd >}}

{{< include ../exercises/_exercises-first-steps-git.qmd >}}

## Slides

{{< include _print-to-pdf.qmd >}}

```{=html}
<iframe width="100%" height=500 src="slides_session03.html"></iframe>
```

## Cheatsheet

### Setup

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
knitr::kable(table_cheatsheet(name = "config"), format = "markdown", row.names = FALSE)
```

### First steps with Git

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
knitr::kable(table_cheatsheet(name = "basic"), format = "markdown", row.names = FALSE)
```
